\documentclass{letter}
\usepackage{hyperref}

% Enconding
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

%\usepackage[portuguese]{babel}

\signature{Vitor Vasconcelos Araújo Silva}
\address{Rua Tuiuti 4/402 \\ Belo Horizonte - MG \\ 30720-440, BRAZIL \\ vitors.vasconcelos@gmail.com \\ +55 31 99152 6349}

% Acertar fechamento e assinatura para a esquerda
\longindentation=40pt

\begin{document}

\begin{letter}{UAB Recruitment team}

  \opening{Dear Hiring Manager,}
  
  I hold a full-time tenure position since 2006 in the Nuclear Technology Development Centre, a public federal
  research institute, part of Brazilian Nuclear Energy Commission, where I work as a technology
  specialist. My job position is aimed to provided support to full-time researchers, in my case
  related to computer technologies,  what I have been doing since 2011 in the group of Nuclear Reactors Technology.
  Some of my activities consist in co-advising undergraduate and graduate students in computer related
  activities activities. I am also the administrator and responsible
  for the installation of a computer cluster of 180 nodes.
  Other activities consist in collaboration
  to the open source project of a nuclear reactor analysis tool \textit{milonga}, among others.

  
  I got encouraged to apply to this position due to the activities expected to be performed. They not only
  match my experience but they involve some of my main professional interests: high performance computing
  and parallel programming.
  
  At this point of my career, I think I am professionally mature enough to apply my knowledge in a more
  challenging position. There is also another important reason to venture into such change: to work
  as part of a live environment. %Not to mention a different work culture in a different country - an
%  experience which I already had.
  %I am reaching a point professionaly where I have not much time left to try
  %new challenges.
  It is common in my current institute to have people losing their enthusiasm due to the
  poor value given by the superior instances of the government to research activities in the nuclear field.
  Considering this, I clearly believe I do have much more to offer than I am being asked for here.
  It is tempting to rely on a tenure to work without pressure and comfortably, but I still want to do more and
  achieve more. UAB seems a place to do it.
  
  \closing{Kind regards,}

  \ps
  P.S. I would be glad to be interviewed by Skype if it is of your interest: \textbf{vitors.vasconcelos} is my contact on this
  platform.
  
\end{letter}
\end{document}
