\documentclass[11pt]{letter}
\usepackage{hyperref}

% Enconding
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

%\usepackage[portuguese]{babel}

\signature{Vitor Vasconcelos Araújo Silva}
\address{Calle San Clemente 1, Piso 9, Puerta 4\\ Santa Cruz de Tenerife\\ 30008, SPAIN \\ vitors@cdtn.br \\ (+34) 634 807 860}

% Acertar fechamento e assinatura para a esquerda
\longindentation=40pt

\begin{document}

\begin{letter}{University of Salerno/ISISLab}

  \opening{Dear Prof. Biagio Cosenza,}
  
  I hold a full-time position since 2009 in the Nuclear Technology Development Centre, a public federal
  research institute, part of Brazilian Nuclear Energy Commission, where I work as a technology
  specialist and hold a permanent position. My job consists mainly on
  providing support to full-time researchers, in my case
  related to computer technologies - software development and infrastructure management - what I have been
  doing since 2011 in the group of Nuclear Reactors Technology, which is formed by no more than a dozen of researchers.
  Some of my activities consist in co-advising undergraduate and graduate students in computer related
  activities and Nuclear Engineering. I am also the administrator and responsible for the installation and management of a
  computer cluster of 9 nodes (with 180 cores). Despite not being part of the academics staff, on the first semester of 2019,
  I taught part of the course ``Computer Science applied to Thermal-Hydraulics'' as invited professor to the post-graduate 
  program of my Institute. A rewarding experience.

  Other of my activities consist in work on research/technical projects which are the study of
  feasibility of GPU utilization by a Monte Carlo Nuclear code and the development of
  a simple visualization software for it. %upcoming activity is the study on the feasibility of digital neutron imaging on the TRIGA research reactor of my Institute.
  Since January 2020 I am on sabbatical unpaid leave initially planned to last one year but of possible extension.
    
  I got encouraged to apply to this position due to the activities expected to be performed. One of my professional
  passions is software development and despite being able to keep doing that in the last 12 years, it has been only
  a complementary task among my activities. I am aware that this can be a disadvantage for this position. However, in my favor, I have the experience on being involved in research for the last 9 years. I also worked full-time as a software developer before starting in my current position. As aforementioned, I am on sabbatical leave since January 2020 and I've been using this time also to update my knowledge in C++ and learning SYCL and parallel programming (practicing in small problems and learning theory). Coincidence or not, I am trying to learn as much as I can about heterogeneous computing since it seems to be the most promising way to take advantage of the new mixed CPU/GPU (and others) high performance computers. I even got an account at Intel's \textit{devcloud} to start playing with its \texttt{DPC++} compiler. The rationale behind these studies on my sabbatical year is to being updated on the upcoming technologies and to be as ready to write software capable of take full advantage of the powerful heterogeneous systems already being used to carry computationally intensive research.

  
%  in a field that shares many commonalities with scientific visualization. Actually, scientific visualization is a fundamental tool for the work on nuclear reactors and nuclear engineering. One example is that the technique used to follow neutrons in the geometry in a Monte Carlo simulation is actually ray tracing. I should also add the during my master's I was member of the Computer Graphics Laboratory (UFRJ - Brazil) and that the concepts of the field are no strange to me. It is worth mentioning that I worked full-time as a software developer before starting in my current position.

  

%  These not only
%  match my experience but involve some of my main professional interests: high performance computing and
%  software development. My attention was hooked by the opportunity to work with staff and students on installing
%  and optimizing software and workflows. %I know that software development is only a complementary task on the
  %duties of this position.
%  My recent experience on projecting, installing and managing a professional
%  cluster (a small one, but professional on the sense of equipment and tools employed, like a distributed file-system)
%  gave me a new perspective on the field of HPC infrastructure and I became really interested on it. As a matter of fact, the activities listed on the job summary for this position are pretty much the activities I carry on a daily basis, but scaled to a whole new level, from a small scientific team to a whole university community. Certainly challenging but also exciting.
  
  At this point of my career, I think I am professionally mature enough to move back into software development in a challenging position. There is also another important reason to venture into such change: being involved in different work culture in a different country - an experience I already had - and which I firmly believe is a driving force on getting better as a professional. I must also mention that the incertitudes in my country for the near future are another motivation in looking for a position where I can, at the same time, expand the horizons of my knowledge, be involved in a more diverse scientific community and postpone my return to Brazil.% to the end of the work contract in the event of being selected for the position.

%  Detailed information on my technical skills is provided in my CV, but I would like to mention that I have been using part of my sabbatical time to study heterogeneous computing using SYCL, updating my knowledge in C++ to standards 14 and 17 and also to improve my knowledge of VTK library. 

  %, a huge part of my daily activities are done in front of a Linux terminal window writing shell scripts, managing a small HPC cluster and programming.
%  I believe it is worth mentioning I am entitled to ask for a non-payed leave lasting for a maximum of three years,
%  which I intend to use 
  %I am reaching a point professionaly where I have not much time left to try
  %new challenges.
%  It is common in my current institute to have people losing their enthusiasm due to the lack of
%  poor value given by the superior instances of the government to research activities in the nuclear field.
  Considering this, I believe I can both continue developing my professional skills while providing high quality work
  for the ISISlab at the University of Salerno.
  
  \closing{Kind regards,}

%  \ps
%  P.S. I would be glad to be interviewed by Skype if it is of
%  your interest: \textbf{vitors.vasconcelos} is my contact on this
%  platform.
  
\end{letter}
\end{document}
